---
title: "Graphical networks with stabs"
author: "Richard Beare"
date: "20 September 2016"
output:
  html_document:
    keep_md: yes
---

<!--
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Using stability selection for graphical models}
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
read_chunk(system.file("stabs_graphs.R", package="stabs"))
```

# Introduction

Tests of modifications to stabs to support graphical networks.

Some minor modifications to the stabs internals to support estimation of inverse covariance
structures. Here are some tests:

```{r, Setup, echo=TRUE, message=FALSE}
library(stabs)
if (!require(huge)) {
  stop("Need package huge for generating test data")
}
if (!require(QUIC)) {
  stop("Need package QUIC")
}
if (!require(igraph)) {
  stop("Need package igraph")
}
N <- 200
set.seed(10010)
dat.hubs <- huge.generator(n=N, d=40, graph="hub")
set.seed(10010)
dat.cluster <- huge.generator(n=N, d=40, graph="cluster")
set.seed(10010)
dat.rand <- huge.generator(n=N, d=40, graph="random")
```

## Generate some test data using _huge_

```{r, PlotHubs}
plot(dat.hubs)
```
```{r, PlotClust}
plot(dat.cluster)
```
```{r, PlotRand}
plot(dat.rand)
```

## Create wrappers for graphical lasso functions (QUIC)

```{r, StabsFunction}
## this is the wrapper function for QUIC
quic.graphical_model
```

## Run stabs
Note that we don't supply a "y" argument, and that we are using a graphical model fitfun. 
```{r, StabsRun}
pcutoff <- 0.75
PFER <- 10
s.hubs <- stabsel(x=dat.hubs$data, fitfun=quic.graphical_model, 
                  cutoff=pcutoff, PFER=PFER)
s.cluster <- stabsel(x=dat.cluster$data, fitfun=quic.graphical_model, 
                  cutoff=pcutoff, PFER=PFER)
s.rand <- stabsel(x=dat.rand$data, fitfun=quic.graphical_model, 
                  cutoff=pcutoff, PFER=PFER)
```
If you want to supply your own fitfun for graphical models then you need to set the function class as follows:
```{r, eval=FALSE}
class(my.graphical_model) <- c(class(my.graphical_model), "graphical_model")
```

## Plot comparisons
```{r,StabsPlot,echo=FALSE}
p1 <- function(stabsout, orig)
{
  ## display comparison of original graph and stabs estimation
  j<- orig$omega * 0
  orig.graph <- graph.adjacency(orig$theta != 0, mode="max", diag=FALSE)
  ut <- upper.tri(j)
  j[ut][stabsout$selected] <- 1
  stabs.graph <- graph.adjacency(j!=0, mode="max", diag=FALSE)
  layout <- layout.fruchterman.reingold(orig.graph)
  par(mfrow=c(1,2))
  plot(orig.graph, layout=layout, edge.color="gray50", vertex.color='red', 
       main="Real graph",  vertex.size = 3, vertex.label = NA)
  plot(stabs.graph, layout=layout, edge.color="gray50", vertex.color='red', 
       main="Stabs estimated graph", vertex.size = 3, vertex.label = NA)
}
```

```{r, StabsPlotHubs}
p1(s.hubs, dat.hubs)
```
```{r, StabsPlotCluster}
p1(s.cluster, dat.cluster)
```
```{r, StabsPlotRand}
p1(s.rand, dat.rand)
```





