---
title: "Graphical networks with stabs"
author: "Richard Beare"
date: "20 September 2016"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{stabs - graphical networks}
output:
  knitr:::html_vignette:
    toc: yes

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
read_chunk(system.file("vignettes/stabs_graphs.R", package="stabs"))
```

# Introduction

Tests of modifications to stabs to support graphical networks.

Some minor modifications to the stabs internals to support estimation of inverse covariance
structures. Here are some tests:

```{r, Setup, echo=FALSE, message=FALSE}

```

## Generate some test data using _huge_

```{r, PlotHubs}

```
```{r, PlotClust}

```
```{r, PlotRand}

```

## Create wrappers for graphical lasso functions (QUIC)

```{r, StabsFunction}

```

## Run stabs
Note that we don't supply a "y" argument, and that we are using a graphical model fitfun. 
```{r, StabsRun}

```
If you want to supply your own fitfun for graphical models then you need to set the function class as follows:
```{r, eval=FALSE}
class(my.graphical_model) <- c(class(my.graphical_model), "graphical_model")
```

## Plot comparisons
```{r,StabsPlot,echo=FALSE}

```

```{r, StabsPlotHubs}

```
```{r, StabsPlotCluster}

```
```{r, StabsPlotRand}

```





