---
title: "Graphical networks with stabs"
author: "Richard Beare & Benjamin Hofner"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Graphical networks with stabs}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
read_chunk(system.file("stabs_graphs.R", package="stabs"))
```

# Introduction

This is a short introduction and test for graphical models with stability 
selection. We first load the relevant packages. We use package **QUIC** to
fit graphical networks:
```{r, Setup, echo=TRUE, message=FALSE, results='hide'}
library(stabs)
library(huge) # Need package huge for generating test data
library(QUIC)
library(igraph)
```

## Generate some test data using _huge_
```{r, echo=TRUE, message=FALSE, results='hide'}
N <- 200
set.seed(10010)
dat.hubs <- huge.generator(n=N, d=40, graph="hub")
set.seed(10010)
dat.cluster <- huge.generator(n=N, d=40, graph="cluster")
set.seed(10010)
dat.rand <- huge.generator(n=N, d=40, graph="random")
```

Next, we can visualize the test data
```{r, PlotHubs, fig.width = 8, fig.height = 8, out.width = "80%"}
plot(dat.hubs)
```
```{r, PlotClust, fig.width = 8, fig.height = 8, out.width = "80%"}
plot(dat.cluster)
```
```{r, PlotRand, fig.width = 8, fig.height = 8, out.width = "80%"}
plot(dat.rand)
```

# Stability selection

To run stability selection on a graphical model, we can simply use the dedicated
`fitfun` called `quic.graphical_model`. Note that we don't supply a `y` argument
to stabsel. 
```{r, StabsRun}
s.hubs <- stabsel(x = dat.hubs$data, fitfun = quic.graphical_model, 
                  cutoff = 0.75, PFER = 10)
s.cluster <- stabsel(x = dat.cluster$data, fitfun = quic.graphical_model, 
                     cutoff = 0.75, PFER = 10)
s.rand <- stabsel(x = dat.rand$data, fitfun = quic.graphical_model, 
                  cutoff = 0.75, PFER = 10)
```

## Plot comparisons

In order to make comparisons possible, we use the following user defined plot 
function
```{r,StabsPlot}
plot_comparison <- function(stabsout, orig) {
    ## display comparison of original graph and stabs estimation
    j <- orig$omega * 0
    orig.graph <- graph.adjacency(orig$theta != 0, mode = "max", diag = FALSE)
    ut <- upper.tri(j)
    j[ut][stabsout$selected] <- 1
    stabs.graph <- graph.adjacency(j != 0, mode = "max", diag = FALSE)
    layout <- layout.fruchterman.reingold(orig.graph)
    
    par(mfrow = c(1,2))
    plot(orig.graph, layout = layout, edge.color = "gray50", vertex.color = 'red', 
         main = "Real graph",  vertex.size = 3, vertex.label = NA)
    plot(stabs.graph, layout = layout, edge.color = "gray50", vertex.color = 'red', 
         main = "Stabs estimated graph", vertex.size = 3, vertex.label = NA)
}
```

Now, we compare the three graphs:
```{r, StabsPlotHubs, fig.width = 8, fig.height = 4, out.width = "80%"}
plot_comparison(s.hubs, dat.hubs)
```
```{r, StabsPlotCluster, fig.width = 8, fig.height = 4, out.width = "80%"}
plot_comparison(s.cluster, dat.cluster)
```
```{r, StabsPlotRand, fig.width = 8, fig.height = 4, out.width = "80%"}
plot_comparison(s.rand, dat.rand)
```
As one can see, the original graphs are resembled by the estimated
graphs rather well in this example.

# User specified `fitfun` for graphical models

For general instruction on how to create a `fitfun` please refer to 
```{r, eval = FALSE}
vignette("Using_stabs", package = "stabs")
```

For an example for grahical model see
```{r}
quic.graphical_model
```

A speciality of graphical models is that the function has an additional class 
`"graphical_model"`. You can set this class immediately after having defined your
`fitfun`, say, `my.graphical_model` as follows:
```{r, eval=FALSE}
class(my.graphical_model) <- c(class(my.graphical_model), "graphical_model")
```
This will avoid that stabsel expects a `y` argument and will change naming
conventions for the resulting selections.
